### 2016-09-29 rebuttal.tex

We deem all the sections in section 3 (now section~\ref{P-sec:features}) to be important core
components of the library. Regarding the supplement sections (previously) 5,
7, and 9---``Sets'', ``Category Theory'', and ``SymPy Live'',
respectively:
\begin{itemize}
\item In SymPy 1.0, the sets module is still in
a relatively infant stage. It is mentioned already in conjunction with the
\texttt{solveset} function. We have added some additional text to the solvers
subsection regarding \texttt{sympy.sets}.

\item The category theory module in SymPy
is very domain specific, and independent of other SymPy modules. It is out of
scope for an architecture paper.

\item The SymPy Live section was short and would be mostly duplicated by the
  paragraph that has been added to the introduction in the paper. We have thus
  removed it.
\end{itemize}

We also consider the supplement sections (previously) 2, 3, 4, and
6---``Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript:

@@

\begin{itemize}
\item The ``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.

\item The ``Logic'' section is alluded to in the ``Assumptions'' subsection,
  but is not discussed in depth in the main manuscript. While the logic
  submodule is indeed important for certain parts of SymPy, we do not consider
  it to be of interest to the general reader. Furthermore, on a technical
  note, the assumptions discussed in the manuscript are the so-called ``old
  assumptions'', which do not use the \texttt{sympy.logic} submodule discussed
  in the supplement (they use an implementation of the Rete algorithm, which
  is separate from \texttt{sympy.logic}). The so-called ``new assumptions'',
  mentioned briefly in the ``Conclusion and Future Work'' section, does use
  it, but we have opted to not discuss this module in depth, as it is still in
  development and not fully usable. We have added some text to the assumptions
  section discussing this and referencing the logic subsection of the
  supplement.

### 2016-09-29 rebuttal.tex

\item The ``Statistics'' module is not a core module and is independent (no
  other SymPy submodules depend on it).
\end{itemize}

The ``Architecture'' section is a key component of the paper. The goal of the
paper is to discuss the architecture and core features of SymPy. It therefore
would be inappropriate to move this section to the supplement. We have
followed the reviewer's advice and moved the architecture section to the end
of the paper, to make the paper easier to follow.
\end{solution}
\end{questions}

\begin{questions}

\question Explaining what Python is (lines 70--72) should go before talking about SymPy as a ``CAS written in Python''. Further, the paper assumes a moderate familiarity with Python (for example, Python's console, OOP, and exceptions), and this should be specified. There should be a short note on the used Python console (\verb|>>>| is the prompt, with the results of computation following immediately in the lines after it). The citation [25] from line 65 should be moved next to ``Python'' in line 70.
\begin{solution}
The citation was moved and footnote~\ref{P-note:prompt} for the Python interactive prompt was
  added where it was used first time. We have also added footnote~\ref{P-note:python} indicating
  a moderate familiarity with Python is assumed.
\end{solution}

### 2016-09-29 introduction.tex
Xref a footnote in the rebuttal

Python is a dynamically typed programming language that has a focus on
ease of use and readability.\footnote{This paper assumes a moderate
  familiarity with the Python programming language.} Due in part to this focus, it has become a popular
language for scientific
computing and data science, with a broad ecosystem of
libraries~\cite{oliphant2007python}. SymPy is itself used by many libraries
and tools to support research within a variety of domains, such as
SageMath~\cite{sagemath} (pure and applied mathematics),
yt~\cite{2011ApJS..192....9T} (astronomy and astrophysics),
PyDy~\cite{gede2013constrained} (multibody dynamics), and
SfePy~\cite{cimrman2014sfepy} (finite elements).

>>>>

Python is a dynamically typed programming language that has a focus on
ease of use and readability.\footnote{\label{note:python}This paper assumes a moderate
  familiarity with the Python programming language.} Due in part to this focus, it has become a popular
language for scientific
computing and data science, with a broad ecosystem of
libraries~\cite{oliphant2007python}. SymPy is itself used by many libraries
and tools to support research within a variety of domains, such as
SageMath~\cite{sagemath} (pure and applied mathematics),
yt~\cite{2011ApJS..192....9T} (astronomy and astrophysics),
PyDy~\cite{gede2013constrained} (multibody dynamics), and
SfePy~\cite{cimrman2014sfepy} (finite elements).
